Seminari su invito indicati con *.
\vspace{0.2cm}

\textcolor{color1}{\textbf{Seminari a conferenze nazionali e internazionali:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{29.} & * & \textit{Emergence of Milky Way structure in the first year of LISA data.}
\newline{}
CERN UniGe Gravitational Wave meeting, Ginevra, Svizzera, 2025/05/23.
\vspace{0.05cm}\\
%
\textbf{28.} &  & \textit{LISA stellar-mass black holes informed by the GWTC-3 population: event rates and parameters reconstruction.}
\newline{}
LISA Astrophysics Working Group Meeting 2024, Garching, Germania, 2024/11/05.
\vspace{0.05cm}\\
%
\textbf{27.} & * & \textit{Astrophysics panel session.}
\newline{}
GRASP: Gravity Shape Pisa 2024, Pisa, Italy, 2024/10/24.
\vspace{0.05cm}\\
%
\textbf{26.} & * & \textit{Beyond Gauss? A more accurate model for LISA astrophysical noise sources.}
\newline{}
Kavli Institute for Cosmology Seminars, Cambridge, Regno Unito, 2024/10/14.
\vspace{0.05cm}\\
%
\textbf{25.} & * & \textit{Beyond Gauss? A more accurate model for LISA astrophysical noise sources.}
\newline{}
Heterogeneous Data and Large Representation Models in Science, Tolosa, Francia, 2024/10/01.
\vspace{0.05cm}\\
%
\textbf{24.} &  & \textit{LISA stellar-mass black holes informed by the GWTC-3 population: event rates and parameters reconstruction.}
\newline{}
15th International LISA Symposium, Dublino, Irlanda, 2024/07/08.
\vspace{0.05cm}\\
%
\textbf{23.} & * & \textit{LISA data analysis: from the stochastic background to the Milky Way.}
\newline{}
11th LISA Cosmology Working Group Workshop, Porto, Portogallo, 2024/06/19.
\vspace{0.05cm}\\
%
\textbf{22.} & * & \textit{An introduction to Bayesian Inference.}
\newline{}
International Pulsar Timing Array Student Week, Milano, Italia, 2024/06/17.
\vspace{0.05cm}\\
%
\textbf{21.} & * & \textit{Statistical challenges in LISA data analysis.}
\newline{}
LAUTARO joint meeting, GSSI-Università di Milano-Bicocca, Milano, Italia, 2024/04/17.
\vspace{0.05cm}\\
%
\textbf{20.} &  & \textit{From mHz to kHz: stochastic background implications on astrophysical sources and population reconstruction.}
\newline{}
LISA Astrophysics working group workshop, Università di Milano-Bicocca, Milano, Italia, 2023/09/13.
\vspace{0.05cm}\\
%
\textbf{19.} &  & \textit{Non-gaussian gravitational wave backgrounds across the GW spectrum.}
\newline{}
XXV Sigrav conference on general relativity and gravitation, SISSA, Trieste, Italia, 2023/09/04.
\vspace{0.05cm}\\
%
\textbf{18.} & * & \textit{LISA SGWB data analysis (session chair).}
\newline{}
Data Analysis Challenges for SGWB Workshop, CERN, Ginevra, Svizzera, 2023/07/19.
\vspace{0.05cm}\\
%
\textbf{17.} & * & \textit{Global Fit and foregrounds.}
\newline{}
LISA SGWB detection brainstorming, Univ. of Geneva, Ginevra, Svizzera, 2023/07/17.
\vspace{0.05cm}\\
%
\textbf{16.} & * & \textit{Beyond functional forms: non-parametric methods. (panelist talk).}
\newline{}
Gravitational-wave populations: What's next?, Università di Milano-Bicocca, Milano, Italia, 2023/07/01.
\vspace{0.05cm}\\
%
\textbf{15.} &  & \textit{The last three years : multiband gravitational-wave observations of stellar-mass binary black holes.}
\newline{}
LISA Astrophysics working group workshop, University of Birmingham, Birmingham, Regno Unito, 2022/06/23.
\vspace{0.05cm}\\
%
\textbf{14.} &  & \textit{The last three years : multiband gravitational-wave observations of stellar-mass binary black holes.}
\newline{}
American Physical Society (APS) April meeting, New York (NY), USA, 2022/04/12.
\vspace{0.05cm}\\
%
\textbf{13.} &  & \textit{Bayesian parameter estimation of stellar-mass black-hole binaries with LISA.}
\newline{}
XXIV Sigrav conference on general relativity and gravitation, Urbino, Italia, 2021/09/08.
\vspace{0.05cm}\\
%
\textbf{12.} &  & \textit{Chirp: a web and smartphone application for visualization of gravitational-wave alerts.}
\newline{}
14th Amaldi Conference on Gravitational Waves, (online) , 2021/07/21.
\vspace{0.05cm}\\
%
\textbf{11.} & * & \textit{Search for lensing signatures in the gravitational-wave observations from the first half of LIGO-Virgo’s third observing run.}
\newline{}
2nd EPS conference on gravitation, (online, per conto della collaborazione LIGO Virgo KAGRA), 2021/05/27.
\vspace{0.05cm}\\
%
\textbf{10.} & * & \textit{Bayesian parameter estimation of stellar-mass black-hole binaries with LISA.}
\newline{}
LISA Data Challenge meeting, (online), 2021/06/17.
\vspace{0.05cm}\\
%
\textbf{9.} & * & \textit{Search for lensing signatures in the gravitational-wave observations from the first half of LIGO-Virgo’s third observing run.}
\newline{}
Webinar on behalf of the LVK collaboration, (online), 2021/05/27.
\vspace{0.05cm}\\
%
\textbf{8.} &  & \textit{Milky Way Satellites Shining Bright in Gravitational Waves.}
\newline{}
13th LISA Symposium, (online), 2020/09/13.
\vspace{0.05cm}\\
%
\textbf{7.} &  & \textit{Constraining the Lensing of Binary Black Holes from Their Stochastic Background.}
\newline{}
LISA Sprint workshop, CCA, Flatiron Institute, New York (NY), USA, 2020/03/04.
\vspace{0.05cm}\\
%
\textbf{6.} &  & \textit{Multiple source detection in GW astronomy: the label switching problem.}
\newline{}
30th Texas Symposium, University of Portsmouth, Portsmouth, Regno Unito, 2019/12/12.
\vspace{0.05cm}\\
%
\textbf{5.} &  & \textit{Non-gaussian Stochastic background search with importance sampling.}
\newline{}
LIGO, Virgo, KAGRA September meeting, Varsavia, Polonia, 2019/09/01.
\vspace{0.05cm}\\
%
\textbf{4.} &  & \textit{An improved detector for non-Gaussian stochastic background.}
\newline{}
Stochastic Background Data Analysis for LISA meeting, Instituto de Fisica Teorica, Madrid, Spagna, 2019/06/01.
\vspace{0.05cm}\\
%
\textbf{3.} &  & \textit{Hierarchical nonparametric density estimation for population inference.}
\newline{}
LIGO, Virgo, KAGRA March meeting, Winsconsin, USA, 2019/03/18.
\vspace{0.05cm}\\
%
\textbf{2.} &  & \textit{Fast Evaluation of Campbell processes N–point correlation functions.}
\newline{}
Astro Hack Week: Data Science for Next-Generation Astronomy, Lorentz Center, Leiden, Paesi Bassi, 2018/08/01.
\vspace{0.05cm}\\
%
\textbf{1.} &  & \textit{Stochastic Gravitational Wave Background Data Analysis for Radler.}
\newline{}
5th LISA Cosmology Working Group workshop, Physicum, University of Helsinki, Helsinki, Finlandia, 2018/06/01.
\vspace{0.05cm}\\
%
\end{longtable} }
\textcolor{color1}{\textbf{Seminari presso istituti di ricerca e dipartimenti universitari:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{10.} & * & \textit{Fast LISA inference using Gaussian processes.}
\newline{}
University of Geneva, Ginevra, Svizzera, 2025/05/21.
\vspace{0.05cm}\\
%
\textbf{9.} & * & \textit{Emergence of Milky Way structure in the first year of LISA data.}
\newline{}
Dipartimento di Fisica, Università di Pisa, Pisa, Italia, 2025/05/16.
\vspace{0.05cm}\\
%
\textbf{8.} & * & \textit{Statistical challenges in GW inference: an application of field theory to direct population reconstruction in LISA.}
\newline{}
APP seminar, SISSA, Trieste, Italia, 2024/05/06.
\vspace{0.05cm}\\
%
\textbf{7.} & * & \textit{GRAF: Gravitational waves data and global fit.}
\newline{}
Dipartimento di Fisica, Università di Milano-Bicocca, Milano, Italia, 2023/12/14.
\vspace{0.05cm}\\
%
\textbf{6.} & * & \textit{LISA global inference: statistical and modelling challenges  for the Milky Way.}
\newline{}
Max Planck Institute for Astrophysics, Garching, Germania, 2023/11/29.
\vspace{0.05cm}\\
%
\textbf{5.} & * & \textit{LISA Global inference: modelling, statistical, and computational challenges.}
\newline{}
Dipartimento di Fisica, Università di Pisa, Pisa, Italia, 2023/10/04.
\vspace{0.05cm}\\
%
\textbf{4.} & * & \textit{Gravitational waves in the many sources, many detectors era.}
\newline{}
Institute for Mathematics and Physics, University of Stavanger, Stavanger, Norvegia, 2022/09/29.
\vspace{0.05cm}\\
%
\textbf{3.} & * & \textit{Stellar mass binary black holes : what, when, and where.}
\newline{}
Astroparticule et cosmologie, Universitè Paris Citè, Paris, Francia, 2022/06/12, (online).
\vspace{0.05cm}\\
%
\textbf{2.} & * & \textit{The last three years: multiband gravitational-wave observations of stellar-mass binary black holes.}
\newline{}
Physics Department, Columbia University, New York (NY), USA, 2022/04/07.
\vspace{0.05cm}\\
%
\textbf{1.} & * & \textit{Set the alarm : Bayesian parameter estimation of stellar-mass black-hole binaries with LISA.}
\newline{}
Sun Yat-sen University, Zhuhai, Cina, 2021/07/30, (online).
\vspace{0.05cm}\\
%
\end{longtable} }
\textcolor{color1}{\textbf{Seminari di divulgazione scientifica e conferenze pubbliche:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{5.} &  & \textit{Onde gravitazionali: ascoltare l'Universo anzichè solo guardarlo.}
\newline{}
Università di Milano-Bicocca, Milano, Italia, 2024.
\vspace{0.05cm}\\
%
\textbf{4.} &  & \textit{An orchestra of lasers and gravitational waves.}
\newline{}
Pint of Science 2024, Milano, Italia, 2024.
\vspace{0.05cm}\\
%
\textbf{3.} &  & \textit{Gravitational-waves in space and on Earth.}
\newline{}
Manchester Museum of Science and Industry, Manchester, Regno Unito, 2018.
\vspace{0.05cm}\\
%
\textbf{2.} &  & \textit{An orchestra of lasers and gravitational waves.}
\newline{}
Manchester Museum of Science and Industry, Manchester, Regno Unito, 2018.
\vspace{0.05cm}\\
%
\textbf{1.} &  & \textit{A Universe of waves.}
\newline{}
Science Cafè, Pontedera, Italia, 2018.
\vspace{0.05cm}\\
%
\end{longtable} }